Data details

### 2022-07-24 analysis/data-details.qmd
Add V-Dem stuff

@@

>>>>

## Pandem

@@

Finally, to measure additional country-level characteristics, we use several variables from the Varieties of Democracy project.

:::{.callout-warning}
Importantly, since these are all measured annually and our main data is daily, these variables act more like country-level fixed effects in our models, capturing the overall level of civil society, human rights, and other characteristics on a given day.
:::

- **CSO repression** (`v2csreprss`)
- **Core civil society index** (`v2xcs_ccsi`): Combination of entry/exit requirements, repression, and participatory environment
- **Political corruption index** (`v2x_corr`): Combination of public sector, executive, legislative, and judicial corruption (less to more, 0–1)
- **Rule of law** (`v2x_rule`)
- **Civil liberties** (`v2x_civlib`)
- **Physical violence** (`v2x_clphy`)
- **Private civil liberties** (`v2x_clpriv`)
- **Political civil liberties index** (`v2x_clpol`)
- **Electoral democracy index** (`v2x_polyarchy`)
- **Regimes of the world scores** (`v2x_regime_amb`)

```{r glimpse-videm}
#| code-fold: false
daily_panel %>% 
  select(country_name, iso3, day, starts_with("v2")) %>%
  glimpse()
```
